Automated Verification of Stand-Alone Solar Photovoltaic Systems

### 2018-11-23 Tex/LaTeX2e Style File/Trindade_IEEE_journal_r2.tex
reviewed section 5 and 6
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

%The charge controller or controller is a set of items (DC-DC converter, MPPT, and switches) and can be defined as the responsible to manage the energy flow to PV system, batteries and loads by collecting information on the battery voltage and knowing the maximum and minimum values acceptable for the battery voltage. %MPPT, or maximum power point tracking, is an electronic control mechanism that maintains the PV operating at the voltage of maximum power. Controllers aim to protect the battery (or batteries) against the excessive charge and discharge \cite{Pinho}, improving its lifetime. 
%
%The resource MPPT, called of maximum power point tracking, is an electronic control mechanism that maintains the PV operating in a voltage that correspond to the voltage of maximum power.
%
%
%As defined by \cite{Hansen} and \cite{Mellit}, all power systems must include a control strategy, which describes the interactions between its components. The use of battery as a storage form implies thus the presence of a charge controller. 
%
In general, there are two main operating modes for the controller \textcolor{blue} {\cite{Rawat}}: normal operating condition, when the battery voltage fluctuates between maximum and minimum voltages; and overcharge or over-discharge conditions, which occur when the battery voltage reaches some critical values.

>>>>

%The charge controller or controller is a set of items (DC-DC converter, MPPT, and switches) and can be defined as the responsible to manage the energy flow to PV system, batteries and loads by collecting information on the battery voltage and knowing the maximum and minimum values acceptable for the battery voltage. %MPPT, or maximum power point tracking, is an electronic control mechanism that maintains the PV operating at the voltage of maximum power. Controllers aim to protect the battery (or batteries) against the excessive charge and discharge \cite{Pinho}, improving its lifetime. 
%
%The resource MPPT, called of maximum power point tracking, is an electronic control mechanism that maintains the PV operating in a voltage that correspond to the voltage of maximum power.
%
%
%As defined by \cite{Hansen} and \cite{Mellit}, all power systems must include a control strategy, which describes the interactions between its components. The use of battery as a storage form implies thus the presence of a charge controller. 
%
In general, there are two main operating modes for the controller~\cite{Rawat}: normal operating condition, when the battery voltage fluctuates between maximum and minimum voltages; and overcharge or over-discharge conditions, which occur when the battery voltage reaches some critical values.
